### 2014-08-15 docs/paper/text/evaluation.tex
list of experiments

\section{Evaluation}

\subsection{I/O comparison}
\begin{alltt}\scriptsize
optimal vs single partition vs. attribute per partition
Compute the I/O for different workloads,
3 values averaged at the end
Also compute the storage...
\end{alltt}

\subsection{LP Solver scalability}
\begin{alltt}\scriptsize
# of attrbutes vs solving time:
\end{alltt}

>>>>

\begin{verbatim}
1) RunningTimeVsNumAttributes:
  x axis: # attributes
  y axis: running time
  series: optimal-nov, optimal-ov, heuristic-nov, heuristic-ov

2) RunningTimeVsNumQueryKinds:
  x axis: num query kinds
  y axis: running time
  series: optimal-nov, optimal-ov, heuristic-nov, heuristic-ov

3) QueryIOVsNumAttributes:
  x axis: # attributes
  y axis: query IO
  series: optimal-nov, optimal-ov, heuristic-nov, heuristic-ov, single-block, per-attribute

4) StorageOverheadVsNumAttributes:
  x axis: # attributes
  y axis: storage overhead
  series: optimal-nov, optimal-ov, heuristic-nov, heuristic-ov, single-block, per-attribute

5) QueryIOVsStorageOverheadThreshold:
  x axis: query overhead threshold
  y axis: query IO
  series: optimal-nov, optimal-ov, heuristic-nov, heuristic-ov, single-block, per-attribute

6) StorageOverheadVsStorageOverheadThreshold:
  x axis: query overhead threshold
  y axis: storage overhead
  series: optimal-nov, optimal-ov, heuristic-nov, heuristic-ov, single-block, per-attribute

7) QueryIOVsNumQueryKinds:
  x axis: num query kinds
  y axis: query IO
  series: optimal-nov, optimal-ov, heuristic-nov, heuristic-ov, single-block, per-attribute

8) StorageOverheadVsNumQueryKinds:
  x axis: num query kinds
  y axis: storage overhead
  series: optimal-nov, optimal-ov, heuristic-nov, heuristic-ov, single-block, per-attribute

9) QueryIOVsAttributeSizeSkew:
  x axis: attribute size skew
  y axis: query IO
  series: optimal-nov, optimal-ov, heuristic-nov, heuristic-ov, single-block, per-attribute

10) StorageOverheadVsAttributeSizeSkew:
  x axis: attribute size skew
  y axis: storage overhead
  series: optimal-nov, optimal-ov, heuristic-nov, heuristic-ov, single-block, per-attribute

11) QueryIOVsQueryLength:
  x axis: mean query length
  y axis: query IO
  series: optimal-nov, optimal-ov, heuristic-nov, heuristic-ov, single-block, per-attribute

12) StorageOverheadVsQueryLength:
  x axis: mean query length
  y axis: storage overhead
  series: optimal-nov, optimal-ov, heuristic-nov, heuristic-ov, single-block, per-attribute

13) QueryIOVsQueryFreqSkew:
  x axis: query freq skew
  y axis: query IO
  series: optimal-nov, optimal-ov, heuristic-nov, heuristic-ov, single-block, per-attribute

14) StorageOverheadVsQueryFreqSkew:
  x axis: query freq skew
  y axis: storage overhead
  series: optimal-nov, optimal-ov, heuristic-nov, heuristic-ov, single-block, per-attribute
\end{verbatim}
